Implementation and Evaluation of the Simple Network Management Protocol over IEEE 802.15.4 Radios under the Contiki Operating System\\ MSc. Thesis Proposal

### 2010-01-31 doc/msc-proposal/msc-snmp.tex
proposal: snmp operations

The Trap is sent by an agent to a manager and indicates that an event has occurred or a certain condition is present. There is no confirmation associated with this notification delivery mechanism for this operation. The Inform operation provides a confirmed notification delivery mechanism. Finally, the Report operation can be used internally to allow SNMP engines to communicate with each other for error notifications and clock synchronization.

>>>>

The Trap is sent by an agent to a manager and indicates that an event has occurred or a certain condition is present. There is no confirmation associated with this notification delivery mechanism. The confirmed notification delivery mechanism is provided by the Inform operation. Finally, the Report operation can be used internally to allow SNMP engines to communicate with each other for error notifications and clock synchronization.
